Supplementary Information

### 2023-12-18 supplement.Rmd
QH comments included

Using the HMM-full 5 state model, we can plot the transition probabilities of the model for pre and post-intervention as well as pre- and post-control manipulation separately Figure \ref{fig:plotTransitionsSupp}). This allows us to see how the transition probabilities between latent states change across Games and Condition.

>>>>

Using the HMM-full 6 state model, we can plot the transition probabilities of the model for pre and post-intervention as well as pre- and post-control manipulation separately Figure \ref{fig:plotTransitionsSupp}). This allows us to see how the transition probabilities between latent states change across Games and Condition.
